Keeping and discarding players

### 2020-08-03 inst/retain.Rmd
bugfix, last column interpreted wrongly as points
points -> misslast
get rid of that stupid 'misslast' argument
update to reflect removal of keep()

Functions `keep()` and `keep_flawed()` can be confusing, here is a
tiny example that should clarify things.  We will use a subset of
`skating_table`:

@@

Object `jj` does not function as a rank table because the entries are
not sequential.  We need to convert it:

@@

```{r}
OT <- ordertable2supp(a,misslast=FALSE)
OT
```

[note carefully how `misslast=FALSE` is needed here].  Now suppose we
are interested only in the first two competitors, `a` and `b`.  There
are two ways to discard competitor `c`, namely `keep()` and
`keep_flawed()`, which do slightly different things.  First, `keep()`:

@@

Above, function `keep_flawed()` has effectively taken `OT`, set `c=0`,
and then discarded the `c^5` term.  This process, while natural, has
the effect of replacing `(a+c)^-4` with `a^-4`, which has no natural
probabilistic interpretation: we are ignoring `c`'s victories but
nevertheless interpreting joint strength term on the denominator [viz
`a+c`] as a *loss* for `a`.  We will now use function `keep()`, which
operates on order tables:

```{r}
RA <- keep(a,1:2)
RA
```

Looking at object `ra` we see six comparisons, of which `a` wins 5 and
`b` wins 1.

```{r}
OR <- ordertable2supp(RA,misslast=FALSE)
OR
```

Above, object `or` is a perfectly sensible likelihood function.  What
happens if we keep only `a`?

```{r}
keep_flawed(OR,1)
```

>>>>

Function `keep_flawed()` can be confusing.  Originally, the package
included a function `keep()` but this used flawed logic, hence the
name of its replacement.  Here is a tiny example that should clarify
things.  We will use a subset of `skating_table`:

@@

Above, rows of object `jj` correspond to competitors and columns to
judges.  Object `jj` does not function as a rank table because the
entries are not sequential.

We could convert explicitly:

@@

```{r}
OT <- ordertable2supp(a)
OT
```

(function `ordertable2supp()` does this automatically, so
`ordertable2supp(jj)` would have given the same result).  Now suppose
we are interested only in the first two competitors, `a` and `b`,
which are competitors 1 and 2.

@@

Above, function `keep_flawed()` has effectively taken `OT`, set `c=0`,
and then discarded the `c^5` term.  This process, while natural, has
the effect of replacing `(a+c)^-4` with `a^-4`, which has no natural
probabilistic interpretation: we are ignoring `c`'s victories but
nevertheless interpreting joint strength term on the denominator [viz
`a+c`] as a *loss* for `a`.

What happens if we keep only `a`?

```{r}
keep_flawed(OT,1)
```
